---
title: "p8105_hw1_ls3751"
output: github_document
---

_Load required packages_
```{r setup, message = FALSE}
library(tidyverse)
library(palmerpenguins)
```


## Problem 1

#### 1.1 Data frame

```{r sample_df, collapse = TRUE}
sample_df <- tibble(
  vec_norm = rnorm(10), 
  vec_logical = vec_norm > 0,
  vec_char = LETTERS [1:10],
  vec_factor = factor(c("A","A","A","B","B","B","B","B","C","C"))
)
```

#### 1.2 Calculating the mean of each variable

```{r, collapse = TRUE}
mean(pull(sample_df,vec_norm))
mean(pull(sample_df,vec_logical))
mean(pull(sample_df,vec_char))
mean(pull(sample_df,vec_factor))
```

__Numeric__ and __logical__vectors did generate the mean. It turns out the the mean of __character vector__ and __factor vector__ returns __NA__. Given the mean of logical vector is `r mean(pull(sample_df,vec_logical))` and the number of TRUE is `r length(sample_df$vec_logical[sample_df$vec_norm>0])`,it is reasonable to assume that True equals to 1 and False equals to 0 in the logical vector.

#### 1.3 convert vectors

##### try as.numeric function
```{r, eval = FALSE}
as.numeric(pull(sample_df,vec_norm))
as.numeric(pull(sample_df,vec_logical))
as.numeric(pull(sample_df,vec_char))
as.numeric(pull(sample_df,vec_factor))
```

The result supports the assumption that TRUE equals to 1 while FALSE equals to 0. The character vector failed to transform to numeric manner. The factor variable, however, was digitialized according to levels.

##### convert logical vector into other form and calculate

```{r, warning = FALSE, results = 'hide'}
#convert the logical vector to numeric, and multiply the random sample by the result
as.numeric(pull(sample_df,vec_logical))*pull(sample_df,vec_norm)
#convert the logical vector to a factor, and multiply the random sample by the result
as.factor(pull(sample_df,vec_logical))*pull(sample_df,vec_norm)
#convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
factor_vec = as.factor(pull(sample_df,vec_logical))
as.numeric(factor_vec)*pull(sample_df,vec_norm)
```

## Problem 2

#### 2.1 Load the pengins dataset

```{r}
data("penguins", package = "palmerpenguins")
```

#### 2.2 Description of the penguins dataset

##### Overview

> The penguins dataset has `r ncol(penguins)` variables, including `r names(penguins)`; It has __`r nrow(penguins)`__ rows and __`r ncol(penguins)`__ columns; The mean flipper length is `r round(mean(pull(penguins,flipper_length_mm), na.rm = T), digits = 2)` mm.

 
*   The variable __species__ is a `r class(penguins$species)` variable, with `r nlevels(penguins$species)` levels: `r levels(penguins$species)`.
*   The variable __island__ is a `r class(penguins$island)` variable, with `r nlevels(penguins$island)` levels: `r levels(penguins$island)`.
*   The variable __bill_length_mm__ is a `r class(penguins$bill_length_mm)` variable (Max: `r max(penguins$bill_length_mm, na.rm = T)`, Min: `r min(penguins$bill_length_mm, na.rm = T)`, Mean: `r round(mean(penguins$bill_length_mm, na.rm = T), digits = 2)`, Median: `r median(penguins$bill_length_mm,na.rm = T)`).
*   The variable __bill_depth_mm__ is a `r class(penguins$bill_depth_mm)` variable (Max: `r max(penguins$bill_depth_mm, na.rm = T)`, Min: `r min(penguins$bill_depth_mm, na.rm = T)`, Mean: `r round(mean(penguins$bill_depth_mm, na.rm = T),digits = 2)`, Median: `r median(penguins$bill_depth_mm,na.rm = T)`).
*   The variable __flipper_length_mm__ is a `r class(penguins$flipper_length_mm)` variable (Max: `r max(penguins$flipper_length_mm, na.rm = T)`, Min: `r min(penguins$flipper_length_mm, na.rm = T)`, Mean: `r round(mean(penguins$flipper_length_mm, na.rm = T),digits = 2)`, Median: `r median(penguins$flipper_length_mm,na.rm = T)`).
*   The variable __body_mass_g__ is a `r class(penguins$body_mass_g)` variable (Max: `r max(penguins$body_mass_g, na.rm = T)`, Min: `r min(penguins$body_mass_g, na.rm = T)`, Mean: `r round(mean(penguins$body_mass_g, na.rm = T),digits = 2)`, Median: `r median(penguins$body_mass_g,na.rm = T)`).
*   The variable __sex__ is a `r class(penguins$sex)` variable, with `r nlevels(penguins$sex)` levels: `r levels(penguins$sex)`.
*   The variable __year__ is a `r class(penguins$year)` variable (Max: `r max(penguins$year, na.rm = T)`, Min: `r min(penguins$year, na.rm = T)`,  Median: `r median(penguins$year,na.rm = T)`).

*(excluded the missing values)*

#### 2.3 Plotting and exporting

##### Flipper_length_mm (y) vs bill_length_mm (x)

```{r scatterplot,collapse = TRUE, warning = FALSE}
plot_flipper_billL <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
plot_flipper_billL
```
*(excluded the missing values)*


##### Export and save the plot

```{r png_export, warning = FALSE}
ggsave('plot_flipper_billL.png', plot = plot_flipper_billL)
```

